---
title: "Eating Out"
author: "Alondra Garcia"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The data comes from the 1998 General Social Survey answer this question

$H_0$ There is no difference among the various races with frequency of eating out  
$H_A$ There is a statistical difference between at least two races with the frequency of eating out  


```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
GSS <-read.dta(file="GSS1998.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,age,eatout)
mydata <- na.omit(mydata)
```

## Methods

response variable is categorical: dine out last week? yes or no

Explanatory variable is race, it too is a categorical variable.  
So we used CAT~CAT

Inference: Chi-square and fisher exact tests

# Descriptive summaries

## Graphical summary

## barchart

```{r}
barchartGC(~race + eatout,data=mydata)
barchartGC(~race + eatout,data=mydata, type="percent")

```
According to the chart white people eat out more then black and other races. 80 percent of white people said yes to eating out. Less then 20 percent said no.

## Numerical summary

```{r}
table1 <- xtabs(~race + eatout, data=mydata)
rowPerc(table1)
colPerc(table1)
```

This table shows that white people eat out about 83.11 percent then the other races.

# Results

# Inferential

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

Chi-squared test shows that the p-vaule is 0.000002287
Therefore we reject the null hypothesis because the p-value is so small that if the null hypothesis were in fact true very it would be very unusual to get a p-vaule that small.

```{r}
fisherXY(mydata$race,mydata$eatout)
```

According to the chart there is no significant difference in frequency of eating out between black and other races because the p-vaule is very small.
The odds ratio is 2.2 between white and black race, they are twice likely to eat out then black races.
The odd ratio between white and other races is 1.9 more then likely to eat out.

## Conclusion

In conclusion there is a difference between at least two races with the frequency of eating out. 




